Analysis of Prenatal Depression and Anxiety during Covid-19

### 2024-03-25 outputs/paper.qmd
some improvements on figures

---
title: ""
format: pdf
date: "24 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/Prenatal_Mental_Health"
bibliography: references.bib
toc: true
---

```{r}
#| include: false
library(arrow)
library(readr)
library(here)
library(ggplot2)
library(janitor)
library(rstanarm)
library(dplyr)
library(modelsummary)
library(broom)
library(knitr)
```

@@

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-income_age
#| fig-cap: The Distribution of Age Groups and Household Income for Pregnant Participants
# Pastel1
clean_data |>
  ggplot(mapping = aes(x = household_income, fill = age_group)) +
  geom_bar(position = "dodge2") + 
  theme(legend.position = "bottom") +
  scale_fill_brewer(palette = "Set2") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  labs(x = "Household Income in 2019", y = "Number of Observations", fill = "Age Group") 
```
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-income
#| tbl-cap: Levels of Depression and Anxiety Among Different Income Groups
clean_data |> group_by(household_income) |> 
  summarise(average_depression = mean(EPDS), average_anxiety = mean(PROMIS)) |> 
  rename("Household Income in 2019" = household_income, 
         "Average Level of Depression" = average_depression, 
         "Average Level of Anxiety" = average_anxiety) |>
  kable()
```

@@

```{r}
#| label: fig-month
#| fig-cap: Distribution of Levels of Depression and Anxiety by Month
#| echo: false
#| warning: false
#| message: false
#| layout-ncol: 2
#| fig-subcap: ["Distribution of Edinburgh Postnatal Depression Scale Scores by Month", "Distribution of Promis Anxiety Scores by Months"]
clean_data |>
  ggplot(aes(x = month, y = EPDS)) +
  geom_boxplot() +
  theme_classic()

clean_data |>
  ggplot(aes(x = month, y = PROMIS)) +
  geom_boxplot() +
  theme_classic()
```

>>>>

---
title: "Analysis of Prenatal Depression and Anxiety during Covid-19"
author: 
  - Boxuan Yi
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: ""
date: "24 March 2024"
date-format: "D MMMM YYYY"
number-sections: true
thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/Prenatal_Mental_Health"
bibliography: references.bib
toc: true
---
# Introduction
```{r}
#| include: false
library(arrow)
library(readr)
library(here)
library(ggplot2)
library(janitor)
library(rstanarm)
library(dplyr)
library(modelsummary)
library(broom)
library(knitr)
```

@@

# Data

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-income_age
#| fig-cap: The Distribution of Age Groups and Household Income for Pregnant Participants
# Pastel1
clean_data |>
  ggplot(mapping = aes(x = household_income, fill = age_group)) +
  geom_bar(position = "dodge2") + 
  theme(legend.position = "bottom") +
  scale_fill_brewer(palette = "Set2") +
  theme(axis.text.x = element_text(angle = 50, hjust = 1)) +
  labs(x = "Household Income in 2019", y = "Number of Observations", fill = "Age Group") 
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-income
#| tbl-cap: Levels of Depression and Anxiety Among Different Income Groups
clean_data |> group_by(household_income) |> 
  summarise(average_depression = mean(EPDS), average_anxiety = mean(PROMIS)) |> 
  rename("Household Income in 2019" = household_income, 
         "Average Level of Depression" = average_depression, 
         "Average Level of Anxiety" = average_anxiety) |>
  kable()
```

@@

```{r}
#| label: fig-month
#| fig-cap: Distribution of Levels of Depression and Anxiety by Month
#| echo: false
#| warning: false
#| message: false
#| layout-ncol: 2
#| fig-subcap: ["Distribution of Edinburgh Postnatal Depression Scale Scores by Month", "Distribution of Promis Anxiety Scores by Months"]
clean_data |>
  ggplot(aes(x = month, y = EPDS)) +
  geom_boxplot() + ylim(0,1)

clean_data |>
  ggplot(aes(x = month, y = PROMIS)) +
  geom_boxplot() + ylim(0,1)
```
